A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-02-16 imaging_demo/ms.tex
Merge mnras branch on to arxiv branch
From b8e3bc0 (arxiv) + 2add9d8 (mnras):
======================================

Merge mnras branch on to arxiv branch

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
% \documentclass[a4paper,fleqn,usenatbib]{../mnras}
\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

Fig.~\ref{fig:MOFF-flowchart} shows the flowchart for MOFF imaging. The
propagated electric fields are shown on the left at different time stamps,
$t_1\ldots t_\textrm{M}$. At each time stamp, the electric fields measured by
antennas are denoted by $E_1(t)\ldots E_\textrm{N}(t)$. The F-engine performs a
temporal Fourier transform on the electric field time-series to obtain electric
field spectra $\widetilde{E}_1(f)\ldots \widetilde{E}_\textrm{N}(f)$ 
($\widetilde{\mathbf{E}}(\mathbf{a})$ in matrix notation) for each of the 
antennas. Each of the complex antenna gains are calibrated to correct the 
corresponding electric field spectra. These calibrated electric fields are 
gridded using an antenna-based gridding convolution function after which it is 
spatially Fourier transformed and squared to obtain an image cube for every time 
stamp. These images are then time-averaged to obtain the accumulated image 
$I(f)$ ($\mathbf{I}(\hat{\mathbf{s}})$ in matrix notation).
\begin{figure}
  \includegraphics[width=\columnwidth]{figure1}
  % \includegraphics[width=\columnwidth]{MOFF_flowchart}
  % \includegraphics[width=\columnwidth]{MOFF_flowchart.eps}
  \caption{A flowchart of MOFF imaging in EPIC. The propagated electric fields
    shown on the left are measured as time-series $E_1(t)\ldots E_\textrm{N}(t)$
    by the antennas $\textrm{A}_1\ldots \textrm{A}_\textrm{N}$ which are then 
    Fourier transformed by the F-engine to produce electric field spectra 
    $\widetilde{E}_1(f)\ldots \widetilde{E}_\textrm{N}(f)$. They are calibrated 
    and gridded. The gridded electric fields $\widetilde{E}_\textrm{g}(f)$ from 
    each time series are imaged to produce images 
    $I_1(f)\ldots I_\textrm{M}(f)$. These images are time-averaged to obtain the 
    final image $I(f)$.}
  \label{fig:MOFF-flowchart}
\end{figure}

Fig.~\ref{fig:FX-flowchart} shows the flowchart for a visibility-based software 
holographic imaging from a FX correlator. The antenna-based F-engine is identical 
to that in the MOFF processing. The electric field spectra from each antenna are 
then cross-multiplied in the X-engine with those from all other antennas to 
obtain the visibilities $\widetilde{V}_\textrm{p}(f)$ ($\mathbf{m}(\mathbf{v})$ 
in matrix notation). They are calibrated and time-averaged to obtain 
$\langle \widetilde{V}_\textrm{p}(f)\rangle$ which are then gridded and imaged to 
obtain the image $I(f)$. The $I(f)$ obtained from both techniques are 
theoretically identical as explained in \S\ref{sec:math}.
\begin{figure}
  \includegraphics[width=\columnwidth]{figure2}
  % \includegraphics[width=\columnwidth]{FX_flowchart}
  % \includegraphics[width=\columnwidth]{FX_flowchart.eps}
  \caption{A flowchart of visibility-based software holographic imaging in EPIC. 
    The FX process flow shares the F-engine with the MOFF process. Following the 
    F-engine, the electric fields pass through the X-engine to produce 
    visibilities $\widetilde{V}_\textrm{p}(f)$ which are calibrated and 
    time-averaged. Then they are gridded to obtain the gridded visibilities 
    $\widetilde{V}_\textrm{g}(f)$ which are then Fourier transformed to obtain 
    the image, $I(f)$.}
  \label{fig:FX-flowchart}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure3}
  % \includegraphics[width=\columnwidth]{a2g_mapping}
  % \includegraphics[width=\columnwidth]{a2g_mapping.eps}
  \caption{Block diagram of an antenna-to-grid mapping. A sparse block-diagonal
    matrix of total size $\Ngrid\times \Nant$ is created where each
    block contains roughly the number of pixels covered by the respective kernel.
    The antenna aperture illumination kernels do not have to be identical to each
    other. A discrete set of arbitrarily placed antennas are now placed on to a
    regular grid.}
  \label{fig:a2g-mapping}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure4}
  % \includegraphics[width=\columnwidth]{F-engine}
  % \includegraphics[width=\columnwidth]{F-engine.eps}
  \caption{Block diagram of a F-engine. The electric field data streams from
    antennas are Fourier transformed in parallel to generate electric field
    spectra.}
  \label{fig:f-engine}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure5}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam.png}
  \caption{The auto-correlation of weights of a square shaped antenna aperture
    in the $uv$ plane (left) and the corresponding directional antenna power 
    response on the sky (right) in coordinates specified by direction cosines. 
    The antenna auto-correlation weights are normalized to a sum
    of unity yielding a peak response of unity in the antenna's directional
    power pattern on the sky. The color scale for the directional power 
    pattern is logarithmic. The black circle indicates the sky horizon and
    values beyond it are not physical and hence ignored.}
  \label{fig:autocorr_wts_PB}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure6}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed.eps}
  \caption{Dirty images (top) and synthesized beams (bottom) obtained from 
    simulated data using EPIC implementation of antenna-based MOFF algorithm 
    (left) and visibility-based imaging (right). The solid black circles in the
    top panels indicate the simulated source positions. The antenna 
    auto-correlations at zero-spacing have been removed from the MOFF images. 
    The images in either case reconstruct the sources at the right locations 
    with the fluxes expected after multiplication by the antenna power pattern. 
    The synthesized beams from the two algorithms are well matched in size and
    shape. The overall modulation by the power pattern is seen clearly in both
    images.}
  \label{fig:MOFF-FX-image}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure7}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{Comparison of $uv$ plane antenna power response with MOFF (left) and 
    visibility-based imaging (right). The zero-spacing footprint from the $uv$ 
    weights obtained with MOFF has been subtracted. Differences in the void 
    centreed around zero-spacing and other outer regions is due to loss of 
    sampled antenna footprint precision due to coarseness of grid spacing 
    further made severe by the correlation process.}
  \label{fig:MOFF-FX-uvwts}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure8}
  % \includegraphics[width=\columnwidth]{diff_psf_MOFF-FX_test_aperture}
  % \includegraphics[width=\columnwidth]{diff_psf_MOFF-FX_test_aperture.eps}
  \caption{Map of difference between the synthesized beams obtained with the 
    two methods (left) and radial statistics of the synthesized beams and 
    their differences (right). The radial variations of rms of the synthesized 
    beam (gray) and that of the rms of the difference (black) are shown as 
    percentage of the peak synthesized beam. Radially averaged directional 
    antenna power response in absolute scale is shown in red and is to be read 
    with the scale on the right side of the axis. The maximum difference is of 
    the order of a few percent. Amplitude of the rms of the difference is 
    modulated by the power pattern of the antenna.}
  \label{fig:psf-diff}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure9}
  % \includegraphics[width=\columnwidth]{LWA_MOFF_bandavg_image_4_iterations_analytic_aperture}
  % \includegraphics[width=\columnwidth]{LWA_MOFF_bandavg_image_4_iterations_analytic_aperture.eps}
  \caption{Image from LWA TBN data obtained with MOFF imaging using EPIC 
    package after averaging over 20~ms and $\approx 80$~kHz. The x- and y-axes
    denote direction cosines $l$ and $m$ respectively. The antenna voltages
    are compensated for their respective delays. The flux scale is arbitrary.
    Locations of Cyg~A and Cas~A are annotated.}
  \label{fig:LWA-image}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure10}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex multiplies and adds with MOFF and FX. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figure11}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended.eps}
  \caption{Current and planned instruments in parameter space of
    baseline length and number of antennas with MOFF and FX. Line styles of 
    different colors denote different classes of antenna sizes (cyan - 1~m$^2$, 
    blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, 
    red - 740~m$^2$, gray - 5900~m$^2$). Solid line style in each color denotes 
    the maximum number of antennas with the corresponding antenna size that can 
    be packed inside various baseline lengths. The region to the right of the 
    solid lines for corresponding antenna size is physically disallowed. Dashed
    lines of each color denote the boundary to the left of which 
    visibility-based imaging is favoured for the corresponding antenna size. 
    Region inside the wedge enclosed by the solid and dashed lines favours using 
    the MOFF algorithm for the corresponding antenna size. These wedges shift 
    leftward with increasing antenna size. The different antennas are color 
    coded by roughly the class of antenna size they fall into. Thus symbols of 
    one color falling into a wedge of the same color indicates MOFF imaging is 
    advantageous for those telescopes and vice versa. For example, MOFF imaging
    is favoured in HERA-331 and HERA-6769 because they are inside the wedge 
    but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}

@@

\bibliographystyle{mnras}
\bibliography{epic} 
% \bibliography{../epic} 
% \input{ms.bbl}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figureA1}
  % \includegraphics[width=\linewidth]{EPIC-modules}
  % \includegraphics[width=\linewidth]{EPIC-modules.eps}
  \caption{Software architecture of EPIC with core modules, their essential
    attributes and functions. The antenna module forms the fundamental building 
    block. It consists of electric field time-series and spectra and the 
    F-engine that performs a temporal FFT to obtain electric field spectra from 
    the time-series. The interferometer module is made of a pair of antenna 
    modules. Its main function is the X-engine (FX or XF) to produce visibility 
    spectra. The antenna array module is made of all individual antenna modules
    as its components and contains collective properties about the antenna 
    subsystems. Its core function is the creation of antenna-to-grid mapping, 
    gridded aperture weights and electric fields. The interferometer array 
    module is very similar in principle to the antenna array module except it 
    operates on cross-correlations and produces gridded visibilities. The image 
    module takes gridded electric fields or visibilities and performs a 
    two-dimensional spatial FFT (and squares the intermediate image in case 
    of the former) to produce output images. Broadly, the MOFF algorithm is 
    implemented by modules below the horizontal dashed line while the 
    visibility-based imaging uses modules above the line. The exact processing 
    pathway implementing the MOFF algorithm is shown in bolded modules.}
  \label{fig:software-modules}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{../mnras}

@@

Fig.~\ref{fig:MOFF-flowchart} shows the flowchart for MOFF imaging. The
propagated electric fields are shown on the left at different time stamps,
$t_1\ldots t_\textrm{M}$. At each time stamp, the electric fields measured by
antennas are denoted by $E_1(t)\ldots E_\textrm{N}(t)$. The F-engine performs a
temporal Fourier transform on the electric field time-series to obtain electric
field spectra $\widetilde{E}_1(f)\ldots \widetilde{E}_\textrm{N}(f)$ 
($\widetilde{\mathbf{E}}(\mathbf{a})$ in matrix notation) for each of the 
antennas. Each of the complex antenna gains are calibrated to correct the 
corresponding electric field spectra. These calibrated electric fields are 
gridded using an antenna-based gridding convolution function after which it is 
spatially Fourier transformed and squared to obtain an image cube for every time 
stamp. These images are then time-averaged to obtain the accumulated image 
$I(f)$ ($\mathbf{I}(\hat{\mathbf{s}})$ in matrix notation).
\begin{figure}
  \includegraphics[width=\columnwidth]{MOFF_flowchart}
  % \includegraphics[width=\columnwidth]{MOFF_flowchart.eps}
  \caption{A flowchart of MOFF imaging in EPIC. The propagated electric fields
    shown on the left are measured as time-series $E_1(t)\ldots E_\textrm{N}(t)$
    by the antennas $\textrm{A}_1\ldots \textrm{A}_\textrm{N}$ which are then 
    Fourier transformed by the F-engine to produce electric field spectra 
    $\widetilde{E}_1(f)\ldots \widetilde{E}_\textrm{N}(f)$. They are calibrated 
    and gridded. The gridded electric fields $\widetilde{E}_\textrm{g}(f)$ from 
    each time series are imaged to produce images 
    $I_1(f)\ldots I_\textrm{M}(f)$. These images are time-averaged to obtain the 
    final image $I(f)$.}
  \label{fig:MOFF-flowchart}
\end{figure}

Fig.~\ref{fig:FX-flowchart} shows the flowchart for a visibility-based software 
holographic imaging from a FX correlator. The antenna-based F-engine is identical 
to that in the MOFF processing. The electric field spectra from each antenna are 
then cross-multiplied in the X-engine with those from all other antennas to 
obtain the visibilities $\widetilde{V}_\textrm{p}(f)$ ($\mathbf{m}(\mathbf{v})$ 
in matrix notation). They are calibrated and time-averaged to obtain 
$\langle \widetilde{V}_\textrm{p}(f)\rangle$ which are then gridded and imaged to 
obtain the image $I(f)$. The $I(f)$ obtained from both techniques are 
theoretically identical as explained in \S\ref{sec:math}.
\begin{figure}
  \includegraphics[width=\columnwidth]{FX_flowchart}
  % \includegraphics[width=\columnwidth]{FX_flowchart.eps}
  \caption{A flowchart of visibility-based software holographic imaging in EPIC. 
    The FX process flow shares the F-engine with the MOFF process. Following the 
    F-engine, the electric fields pass through the X-engine to produce 
    visibilities $\widetilde{V}_\textrm{p}(f)$ which are calibrated and 
    time-averaged. Then they are gridded to obtain the gridded visibilities 
    $\widetilde{V}_\textrm{g}(f)$ which are then Fourier transformed to obtain 
    the image, $I(f)$.}
  \label{fig:FX-flowchart}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{a2g_mapping}
  % \includegraphics[width=\columnwidth]{a2g_mapping.eps}
  \caption{Block diagram of an antenna-to-grid mapping. A sparse block-diagonal
    matrix of total size $\Ngrid\times \Nant$ is created where each
    block contains roughly the number of pixels covered by the respective kernel.
    The antenna aperture illumination kernels do not have to be identical to each
    other. A discrete set of arbitrarily placed antennas are now placed on to a
    regular grid.}
  \label{fig:a2g-mapping}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{F-engine}
  % \includegraphics[width=\columnwidth]{F-engine.eps}
  \caption{Block diagram of a F-engine. The electric field data streams from
    antennas are Fourier transformed in parallel to generate electric field
    spectra.}
  \label{fig:f-engine}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam}
  % \includegraphics[width=\columnwidth]{autocorr_uvwts_pbeam.png}
  \caption{The auto-correlation of weights of a square shaped antenna aperture
    in the $uv$ plane (left) and the corresponding directional antenna power 
    response on the sky (right) in coordinates specified by direction cosines. 
    The antenna auto-correlation weights are normalized to a sum
    of unity yielding a peak response of unity in the antenna's directional
    power pattern on the sky. The color scale for the directional power 
    pattern is logarithmic. The black circle indicates the sky horizon and
    values beyond it are not physical and hence ignored.}
  \label{fig:autocorr_wts_PB}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_10_random_source_positions_4_iterations_test_aperture_zoomed.eps}
  \caption{Dirty images (top) and synthesized beams (bottom) obtained from 
    simulated data using EPIC implementation of antenna-based MOFF algorithm 
    (left) and visibility-based imaging (right). The solid black circles in the
    top panels indicate the simulated source positions. The antenna 
    auto-correlations at zero-spacing have been removed from the MOFF images. 
    The images in either case reconstruct the sources at the right locations 
    with the fluxes expected after multiplication by the antenna power pattern. 
    The synthesized beams from the two algorithms are well matched in size and
    shape. The overall modulation by the power pattern is seen clearly in both
    images.}
  \label{fig:MOFF-FX-image}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed}
  % \includegraphics[width=\columnwidth]{MOFF_FX_comparison_uvwts_test_aperture_zero_spacing_removed.eps}
  \caption{Comparison of $uv$ plane antenna power response with MOFF (left) and 
    visibility-based imaging (right). The zero-spacing footprint from the $uv$ 
    weights obtained with MOFF has been subtracted. Differences in the void 
    centreed around zero-spacing and other outer regions is due to loss of 
    sampled antenna footprint precision due to coarseness of grid spacing 
    further made severe by the correlation process.}
  \label{fig:MOFF-FX-uvwts}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{diff_psf_MOFF-FX_test_aperture}
  % \includegraphics[width=\columnwidth]{diff_psf_MOFF-FX_test_aperture.eps}
  \caption{Map of difference between the synthesized beams obtained with the 
    two methods (left) and radial statistics of the synthesized beams and 
    their differences (right). The radial variations of rms of the synthesized 
    beam (gray) and that of the rms of the difference (black) are shown as 
    percentage of the peak synthesized beam. Radially averaged directional 
    antenna power response in absolute scale is shown in red and is to be read 
    with the scale on the right side of the axis. The maximum difference is of 
    the order of a few percent. Amplitude of the rms of the difference is 
    modulated by the power pattern of the antenna.}
  \label{fig:psf-diff}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{LWA_MOFF_bandavg_image_4_iterations_analytic_aperture}
  % \includegraphics[width=\columnwidth]{LWA_MOFF_bandavg_image_4_iterations_analytic_aperture.eps}
  \caption{Image from LWA TBN data obtained with MOFF imaging using EPIC 
    package after averaging over 20~ms and $\approx 80$~kHz. The x- and y-axes
    denote direction cosines $l$ and $m$ respectively. The antenna voltages
    are compensated for their respective delays. The flux scale is arbitrary.
    Locations of Cyg~A and Cas~A are annotated.}
  \label{fig:LWA-image}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated}
  % \includegraphics[width=\columnwidth]{MOFF_FX_computations_fov_gridding_annotated.eps}
  \caption{Current and planned instruments in parameter space of
    number of complex multiplies and adds with MOFF and FX. The solid line
    is the boundary at which the number of operations with MOFF and 
    visibility-based imaging are equal. MOFF imaging is more efficient for 
    telescopes occupying the left of this line and vice versa. CHIME, HIRAX, 
    SKA1-LC, SKA1-LCD and all the HERA layouts except HERA-19 and HERA-37 lie 
    in the parameter space favoured by MOFF imaging. The dashed line shows the 
    projected trajectory of hypothetical expanded HERA layouts. The dotted line 
    similarly shows hypothetical expanded MWA layouts with more tiles added in 
    the same core. The gray shaded area denotes the projected trajectory of the 
    LWA bounded by LWA1 (left edge), LWA-OV (right edge), current layout 
    (bottom) and a four-fold increase in the number of elements within a 50 per 
    cent increase in the core size (top). Current instruments such as MWA and 
    LOFAR fall in a region favoured by visibility-based imaging.}
  \label{fig:parameter-space-computations-instruments}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended}
  % \includegraphics[width=\columnwidth]{MOFF_FX_crossover_baseline_n-antennas_rho_fov_gridding_legended.eps}
  \caption{Current and planned instruments in parameter space of
    baseline length and number of antennas with MOFF and FX. Line styles of 
    different colors denote different classes of antenna sizes (cyan - 1~m$^2$, 
    blue - 7~m$^2$, purple - 16~m$^2$, green - 28~m$^2$, orange - 150~m$^2$, 
    red - 740~m$^2$, gray - 5900~m$^2$). Solid line style in each color denotes 
    the maximum number of antennas with the corresponding antenna size that can 
    be packed inside various baseline lengths. The region to the right of the 
    solid lines for corresponding antenna size is physically disallowed. Dashed
    lines of each color denote the boundary to the left of which 
    visibility-based imaging is favoured for the corresponding antenna size. 
    Region inside the wedge enclosed by the solid and dashed lines favours using 
    the MOFF algorithm for the corresponding antenna size. These wedges shift 
    leftward with increasing antenna size. The different antennas are color 
    coded by roughly the class of antenna size they fall into. Thus symbols of 
    one color falling into a wedge of the same color indicates MOFF imaging is 
    advantageous for those telescopes and vice versa. For example, MOFF imaging
    is favoured in HERA-331 and HERA-6769 because they are inside the wedge 
    but not so in cases of HERA-19 and HERA-37.}
  \label{fig:parameter-space-bll-nant-instruments}
\end{figure}

@@

\bibliographystyle{mnras}
\bibliography{../epic} 
% \input{ms.bbl}

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{EPIC-modules}
  % \includegraphics[width=\linewidth]{EPIC-modules.eps}
  \caption{Software architecture of EPIC with core modules, their essential
    attributes and functions. The antenna module forms the fundamental building 
    block. It consists of electric field time-series and spectra and the 
    F-engine that performs a temporal FFT to obtain electric field spectra from 
    the time-series. The interferometer module is made of a pair of antenna 
    modules. Its main function is the X-engine (FX or XF) to produce visibility 
    spectra. The antenna array module is made of all individual antenna modules
    as its components and contains collective properties about the antenna 
    subsystems. Its core function is the creation of antenna-to-grid mapping, 
    gridded aperture weights and electric fields. The interferometer array 
    module is very similar in principle to the antenna array module except it 
    operates on cross-correlations and produces gridded visibilities. The image 
    module takes gridded electric fields or visibilities and performs a 
    two-dimensional spatial FFT (and squares the intermediate image in case 
    of the former) to produce output images. Broadly, the MOFF algorithm is 
    implemented by modules below the horizontal dashed line while the 
    visibility-based imaging uses modules above the line. The exact processing 
    pathway implementing the MOFF algorithm is shown in bolded modules.}
  \label{fig:software-modules}
\end{figure*}
